% swim-times-sdd.tex
% Software Design Document for the swim-times program
% IEEE Std 1016-2009 structure
% Compiled with: pdflatex swim-times-sdd.tex

\documentclass[12pt]{article}

\usepackage{geometry}
\geometry{letterpaper, margin=1in}

\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{listings}

\definecolor{castblue}{RGB}{0,48,135}
\definecolor{lightgray}{gray}{0.95}

\lstset{
  basicstyle=\ttfamily\small,
  backgroundcolor=\color{lightgray},
  frame=single,
  framesep=4pt,
  rulecolor=\color{lightgray},
  breaklines=true,
  showstringspaces=false,
  language=C,
  keywordstyle=\bfseries\color{castblue},
  commentstyle=\itshape\color{gray},
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\fancyhead[L]{\small College Area Swim Team}
\fancyhead[R]{\small SDD: swim-times}
\fancyfoot[C]{\thepage}

\titleformat{\section}{\large\bfseries\color{castblue}}{\thesection}{0.5em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\req}[1]{\textbf{#1}}

\begin{document}

% -----------------------------------------------------------------
% Title block
% -----------------------------------------------------------------
\begin{titlepage}
  \centering
  \vspace*{2cm}
  {\Huge\bfseries\color{castblue} Software Design Document\\[0.5em]}
  {\Large swim-times: Automated Swimmer-Times Retrieval System}\\[2em]
  {\large College Area Swim Team (CAST)}\\[0.5em]
  {\normalsize Prepared for: CAST Coaching Staff and Maintainers}\\[0.5em]
  {\normalsize Prepared by: CAST Technology Working Group}\\[2em]
  \begin{tabular}{ll}
    Document identifier: & CAST-SDD-001                                \\
    Revision:            & 1.0                                         \\
    Date:                & April 22, 2026                              \\
    Status:              & Released                                    \\
    Governing standard:  & IEEE Std 1016-2009 (Software Design Descriptions) \\
  \end{tabular}
  \vfill
  {\small\textit{This document is prepared in accordance with the principles
  of rational documentation articulated in D.\,L.\,Parnas and P.\,C.\,Clements,
  ``A Rational Design Process: How and Why to Fake It,''
  \textit{IEEE Transactions on Software Engineering}, vol.\,SE-12, no.\,2,
  pp.\,251--257, February 1986.}}
\end{titlepage}

\tableofcontents
\clearpage

% =================================================================
\section{Introduction}
% =================================================================

\subsection{Purpose}

This Software Design Document (SDD) describes the architecture
and detailed design of the \textbf{swim-times} program.  It
satisfies the design-description function of IEEE~Std~1016-2009
by presenting a set of design views, each tailored to a specific
stakeholder concern.  Together with the Concept of Operations
(CAST-CONOPS-001) and the Software Requirements Specification
(CAST-SRS-001), this document forms the complete development
baseline for swim-times.

\subsection{Scope}

This SDD covers all code that is tangled out of the literate
program \code{swim2/swim-times.w}.  It does not cover the
build system, deployment, or the companion Pandoc-based PDF
report (\code{swim/swim-times.md}); those are described
elsewhere.

\subsection{Relationship to the Parnas--Clements model}

Per Parnas and Clements (1986), this document presents the
design as if it had been derived top-down from requirements,
even though in practice the program evolved through exploratory
prototyping against an undocumented third-party API.  Each
design decision is presented in the form a reader would find
most useful, with the rationale recorded so that future changes
can be evaluated against the original intent.

% =================================================================
\section{Design Stakeholders and Concerns}
% =================================================================

\begin{center}
\begin{longtable}{p{3.5cm}p{3.5cm}p{6cm}}
  \toprule
  \textbf{Stakeholder} & \textbf{Concern} & \textbf{Addressed by view} \\
  \midrule\endhead
  Maintainers     & Module decomposition  & Composition view (\S4.2)        \\
  Maintainers     & Data structures       & Information view (\S4.4)        \\
  Maintainers     & Algorithmic detail    & Algorithm view (\S4.7)          \\
  Coaches/parents & Behaviour at runtime  & Interaction view (\S4.6)        \\
  Integrators     & External interfaces   & Context view (\S4.1) and Interface view (\S4.5) \\
  Auditors        & Security boundaries   & Resource view (\S4.8)           \\
  Reviewers       & Design rationale      & Design rationale (\S5)          \\
  \bottomrule
\end{longtable}
\end{center}

% =================================================================
\section{Design Approach}
% =================================================================

\subsection{Architectural style}

swim-times is a single-process, single-threaded
\emph{pipes-and-filters} architecture realised within one address
space: command-line options flow into an option-parsing stage,
which feeds a swimmer-resolution stage, which feeds a per-event
fetch-parse-sort stage, whose output is serialised by a
formatter to standard output.  Each stage is a CWEB chunk
(or small group of chunks) with a single responsibility.

\subsection{Key design decisions}

\begin{description}[style=nextline]
  \item[D-1: CWEB literate source.]
        The canonical source is \code{swim-times.w};
        \code{swim-times.c} is a build artefact.  This satisfies
        \req{REQ-D-02} and \req{REQ-A-04}.

  \item[D-2: 24-line chunk discipline.]
        No CWEB chunk exceeds twenty-four lines.  Larger logical
        units are decomposed into named sub-chunks.  This satisfies
        \req{REQ-D-03} and improves readability for the typeset
        documentation.

  \item[D-3: String-scanning JSON parser.]
        A purpose-built scanner (\code{scan\_string},
        \code{scan\_long}) is used in place of a third-party
        JSON library.  This satisfies \req{REQ-D-04} and is
        adequate because the Sisense JAQL response shape is
        stable and well-understood.

  \item[D-4: Static bearer token.]
        The Sisense bearer token is a compile-time constant.
        Token rotation is a maintenance event, not a runtime
        operation; this matches \req{REQ-A-02}.

  \item[D-5: Insertion sort.]
        Per-event row counts rarely exceed a few dozen, so
        $O(n^2)$ insertion sort is used in preference to a more
        complex algorithm.  Simpler code, fewer failure modes.
\end{description}

% =================================================================
\section{Design Views}
% =================================================================

% --------------------------- 4.1 ---------------------------------
\subsection{Context view}

\paragraph{External actors.}
\begin{itemize}
  \item \textbf{Operator} --- a coach, parent, or maintainer
        invoking the binary from a shell.
  \item \textbf{Sisense JAQL endpoint} --- the upstream HTTPS
        service at \texttt{usaswimming.sisense.com}.
  \item \textbf{Standard output / standard error} --- the
        downstream sinks that receive table or CSV output and
        diagnostics, respectively.
\end{itemize}

\paragraph{Trust boundary.}
The only trusted external system is the Sisense endpoint, which
serves only public competitive records.  No user-supplied data
crosses a trust boundary; command-line arguments are consumed
internally.

% --------------------------- 4.2 ---------------------------------
\subsection{Composition view}

The program is decomposed into the following top-level CWEB
chunks (the order in which they appear in the tangled output):

\begin{center}
\begin{longtable}{ll}
  \toprule
  \textbf{Chunk} & \textbf{Responsibility} \\
  \midrule\endhead
  \code{Includes}                 & Standard headers, \code{<curl/curl.h>}, \code{<libpq-fe.h>} \\
  \code{Global constants}         & Numeric limits, Sisense token, event table     \\
  \code{Option flags}             & \code{OPT\_*} bitmasks and global option state \\
  \code{Type definitions}         & \code{Buffer}, \code{TimeRow}, \code{Swimmer}
                                    structs                                          \\
  \code{HTTP utilities}           & \code{write\_cb}, \code{post\_json}            \\
  \code{JSON scanner}             & \code{scan\_string}, \code{scan\_long}         \\
  \code{Database connection}      & \code{db\_conn\_string}, \code{db\_open},
                                    \code{db\_close}, \code{db\_insert\_row}        \\
  \code{Person lookup}            & \code{lookup\_person\_key}                     \\
  \code{Times fetch}              & \code{insertion\_sort}, \code{format\_date},
                                    \code{fetch\_times}                            \\
  \code{Offline fetch}            & \code{offline\_fetch} (libpq \code{SELECT})    \\
  \code{Main function}            & Option parsing, swimmer table, \code{main}     \\
  \bottomrule
\end{longtable}
\end{center}

Each top-level chunk is itself a composition of named sub-chunks
to honour the 24-line discipline (D-2).  For example,
\code{post\_json} expands to \code{Initialize curl handle} +
\code{Issue HTTP request and return}; \code{fetch\_times} expands
to five sub-chunks corresponding to URL build, body build, fetch,
parse, and print.

% --------------------------- 4.3 ---------------------------------
\subsection{Dependency view}

\begin{center}
\begin{tabular}{ll}
  \toprule
  \textbf{Caller}       & \textbf{Callee}                              \\
  \midrule
  \code{main}           & \code{parse\_opts\_str}, \code{parse\_events\_str}, \code{print\_usage} \\
  \code{main}           & \code{db\_open}, \code{db\_close} (under \code{store}) \\
  \code{main}           & \code{lookup\_person\_key}, \code{fetch\_times} (online) \\
  \code{main}           & \code{offline\_fetch} (under \code{offline})            \\
  \code{lookup\_person\_key} & \code{post\_json}, \code{scan\_string}, \code{scan\_long} \\
  \code{fetch\_times}   & \code{post\_json}, \code{scan\_string},
                          \code{insertion\_sort}, \code{format\_date},
                          \code{csv\_emit\_field}                        \\
  \code{offline\_fetch} & \code{PQexecParams}, \code{PQgetvalue},
                          \code{insertion\_sort}                          \\
  \code{db\_open}/\code{db\_close} & \code{PQconnectdb}, \code{PQprepare},
                          \code{PQfinish} (libpq)                         \\
  \code{db\_insert\_row} & \code{PQexecPrepared} (libpq)                  \\
  \code{post\_json}     & \code{libcurl} easy interface                  \\
  \code{post\_json}     & \code{write\_cb} (callback)                    \\
  \bottomrule
\end{tabular}
\end{center}

The dependency graph is acyclic.  The two linked external
dependencies are \code{libcurl} (HTTP) and \code{libpq} (Postgres
client library), both linked at build time.  Postgres is reached
\emph{programmatically} via libpq calls --- no external
\texttt{psql} process or shell wrapper is involved (this
realises requirement~\#3 of \texttt{requirements4.txt}).

% --------------------------- 4.4 ---------------------------------
\subsection{Information view (data structures)}

\paragraph{\code{Buffer}.}
A growable heap buffer used to accumulate libcurl response chunks.
Always null-terminated so it can be treated as a C string.

\begin{lstlisting}
typedef struct {
    char  *data;
    size_t size;
} Buffer;
\end{lstlisting}

\paragraph{\code{TimeRow}.}
One swim-time record.  \code{sort\_key} is the Sisense numeric
sort key parsed as a \code{double}; the remaining fields are
fixed-size character arrays sized to comfortably exceed the
longest values observed in production data.

\begin{lstlisting}
typedef struct {
    double sort_key;
    char   time[32];
    char   date[16];
    char   standard[48];
    char   meet[256];
} TimeRow;
\end{lstlisting}

\paragraph{\code{Swimmer}.}
A static configuration record describing how to identify each
tracked swimmer in the Sisense Persons table and, optionally,
the inclusive ISO date window to which results are restricted
(used by \code{ledecky10}, \code{ledecky12}, \code{ledecky14}).
The same physical swimmer may appear in \code{SWIMMERS[]} more
than once with distinct date windows --- this is how the three
Ledecky age-group views are realised.

\begin{lstlisting}
typedef struct {
    const char *search_query;  /* Sisense person-search "contains" */
    const char *match_substr;  /* lowercase substring filter       */
    int         flag;          /* OPT_STELLA, OPT_KALEA, ...       */
    const char *date_min;      /* "YYYY-MM-DD" inclusive (or NULL) */
    const char *date_max;      /* "YYYY-MM-DD" inclusive (or NULL) */
} Swimmer;
\end{lstlisting}

\paragraph{Database schema (\texttt{schema.sql}).}
Persisted rows live in the \texttt{swim\_times} table, whose
columns mirror the seven fields written by the DB-pipe emitter
plus an identity primary key and a \texttt{fetched\_at}
timestamp.  A UNIQUE constraint on
\texttt{(swimmer, event, swim\_time, swim\_date, meet)} prevents
duplicate inserts on repeated \code{store} runs (REQ-F-73).
Two indexes (\texttt{(swimmer, event)} and
\texttt{(event, sort\_key)}) accelerate the \code{offline}
\texttt{SELECT} (REQ-F-71) which filters on swimmer name and
event code and orders by \texttt{sort\_key}.

\paragraph{Global state.}
Three module-level variables hold parsed command-line state:

\begin{itemize}
  \item \code{g\_opts} --- bitmask of \code{OPT\_*} flags.
  \item \code{g\_events[NUM\_EVENTS][32]} --- user-requested
        event codes.
  \item \code{g\_nevents} --- count of valid entries in
        \code{g\_events}.
\end{itemize}

% --------------------------- 4.5 ---------------------------------
\subsection{Interface view}

\paragraph{Command-line interface.}
\begin{itemize}
  \item \code{-o keyword[,keyword\ldots]} --- swimmer and output options.
  \item \code{-e event[,event\ldots]} --- restrict to event codes;
        repeatable.
\end{itemize}

\paragraph{HTTP interface.}
Two POST endpoints are consumed (skipped under \code{offline}):
\begin{itemize}
  \item \texttt{.../aPublicIAAaPersonIAAaSearch/jaql}
        --- person search.
  \item \texttt{.../aUSAIAAaSwimmingIAAaTimesIAAaElasticube/jaql}
        --- times query.
\end{itemize}

Both carry the headers \code{Content-Type: application/json} and
\code{Authorization: Bearer \{SISENSE\_TOKEN\}}.

\paragraph{Database interface.}
Postgres is reached \emph{programmatically} through the
\texttt{libpq} client library (\req{REQ-I-12}) --- no
\texttt{psql} child process and no shell wrapper.  The
connection string is taken from
\texttt{SWIM\_TIMES\_PGCONNINFO} when set, otherwise the
default keyword string
\texttt{dbname=swim-times user=postgres host=localhost port=5432}.
A single \code{PGconn} is opened in \code{db\_open} and reused
for the lifetime of the run.  Two access patterns are needed:
\begin{itemize}
  \item Write (\code{store}): a prepared statement
        \texttt{INSERT INTO swim\_times (\dots) VALUES
        (\$1\dots\$7) ON CONFLICT (swimmer, event, swim\_time,
        swim\_date, meet) DO NOTHING}, executed once per row via
        \code{PQexecPrepared}.  Per-row inserts (rather than a
        single \texttt{COPY}) let \texttt{ON~CONFLICT~DO~NOTHING}
        absorb duplicates one at a time without rolling back the
        whole batch (\req{REQ-F-75}).
  \item Read (\code{offline}): one parameterised
        \texttt{SELECT \dots\ FROM swim\_times WHERE swimmer
        ILIKE \$1 AND event = \$2} per event via
        \code{PQexecParams}; tuples are read with
        \code{PQgetvalue}.
\end{itemize}

\paragraph{Standard output.}
Either a CSV stream (header line followed by data lines) or a
plain-text table (per-event heading, column header, separator,
data rows, blank line).

% --------------------------- 4.6 ---------------------------------
\subsection{Interaction view}

A typical invocation flows through the following sequence:

\begin{enumerate}
  \item \code{main} parses \code{-o} / \code{-e} via \code{getopt}.
  \item Unless \code{offline} is set, \code{main} initialises
        libcurl (\code{curl\_global\_init}).
  \item If either \code{store} or \code{offline} is set,
        \code{main} calls \code{db\_open} which opens a libpq
        connection (\code{PQconnectdb}) and prepares the
        idempotent \code{INSERT \dots\ ON~CONFLICT~DO~NOTHING}
        statement.  Failure under \code{offline} is fatal;
        failure under \code{store} only is logged and persistence
        is silently disabled.
  \item For each entry in \code{SWIMMERS} not masked out by
        \code{g\_opts}, the dispatcher chooses the online or
        offline path:
        \begin{enumerate}
          \item \emph{Online.} \code{lookup\_person\_key} issues
                one POST and returns the \code{PersonKey}.  For
                each requested event (or all default events),
                \code{fetch\_times} issues one POST, parses the
                response into a \code{TimeRow} array, applies the
                \code{Swimmer}'s optional date window, sorts the
                rows, and emits them to stdout, the DB pipe, or
                both per the option mask.
          \item \emph{Offline.} \code{offline\_fetch} runs a
                parameterised \texttt{SELECT \dots\ FROM swim\_times}
                via \code{PQexecParams} for each event, copies
                each tuple into a \code{TimeRow} array, applies
                the date window, sorts, and emits.  No HTTP is
                performed; no child process is spawned.
        \end{enumerate}
  \item \code{main} calls \code{db\_close} (no-op when no
        connection was opened) and, unless \code{offline}, also
        calls \code{curl\_global\_cleanup} before exiting.
\end{enumerate}

% --------------------------- 4.7 ---------------------------------
\subsection{Algorithm view}

\paragraph{JSON scanning.}
\code{scan\_string} locates the next occurrence of the literal
\code{"key"}, advances past the colon and any whitespace, expects
a double-quote, and copies bytes until the matching closing quote
into the output buffer.  \code{scan\_long} is the integer
counterpart, using \code{strtol} on the digits following the colon.
Both functions advance an in/out position pointer so that
sequential scans walk forward through the response without rescan.

\paragraph{Sort.}
\code{insertion\_sort} performs an in-place ascending sort of a
\code{TimeRow} array by \code{sort\_key}.  Chosen over heap or
quick sort because $n$ rarely exceeds 50 and insertion sort has
no recursion, no auxiliary memory, and trivial correctness.

\paragraph{Date reformat.}
\code{format\_date} converts \code{YYYYMMDD} (eight bytes) to
\code{YYYY-MM-DD} (ten bytes plus terminator) by direct byte
copy and hyphen insertion---no \code{sscanf} round-trip required.

% --------------------------- 4.8 ---------------------------------
\subsection{Resource view}

\paragraph{Memory.}
Per-event peak memory is bounded by
$\code{MAX\_TIMES} \times \mathtt{sizeof}(\code{TimeRow})$
(approximately 70~KiB per event), plus the response buffer
(typically 30--80~KiB).  Buffers are freed at end of each
\code{fetch\_times} call; no long-lived heap state accumulates
across events.

\paragraph{Network.}
Each invocation issues at most $4 + (4 \times 31) = 128$ HTTPS
POSTs.  All connections are short-lived; libcurl manages connection
reuse internally where the easy-interface allows.

\paragraph{Credentials.}
The Sisense bearer token is a static const string in the binary.
Token rotation requires editing \code{swim-times.w} and
recompiling.  No filesystem-level credential storage is used.

% =================================================================
\section{Design Rationale}
% =================================================================

\subsection{Why CWEB?}

CWEB satisfies \req{REQ-A-04} (self-documentation) directly: the
typeset \code{swim-times.pdf} is the program's reference
documentation.  Equivalent C-with-comments would have required
maintaining design prose in a separate document, with the
inevitable drift between code and documentation that the
Parnas--Clements paper warns against.

\subsection{Why no JSON library?}

Adding \code{cJSON} or \code{jansson} would introduce a build
dependency and would obscure the small, focused parsing logic
that actually serves the program.  The Sisense response shape is
stable and the scanner has fewer than fifty lines of code; the
cost of a custom scanner is therefore lower than the cost of a
third-party dependency.

\subsection{Why static bearer token?}

The token is read-only against a public dataset; embedding it
matches the actual security posture (low) and avoids the
operational complexity of credential injection.  When USA~Swimming
rotates the token (an event observed only twice in the past two
years), the maintainer recompiles and redeploys.

\subsection{Why insertion sort?}

\req{D-5} addresses this directly.  The complexity argument is
not just about wall-clock time---it is about reading the code:
twelve lines of insertion sort can be verified by eye, whereas a
heap sort cannot.  For $n < 100$ the wall-clock difference is
imperceptible.

\subsection{Why one binary, not two?}

A separate person-search utility was considered but rejected.
The two queries (person search, times query) are always issued
together, and splitting them would force the caller to thread
the \code{PersonKey} through the shell, complicating every
invocation for no gain.

\subsection{Why \texttt{libpq} (programmatic), not \texttt{psql}?}

Earlier revisions reached Postgres by spawning a child
\texttt{psql} (via \texttt{pg.sh}) and either piping CSV into
\texttt{COPY \dots\ FROM~STDIN} or capturing pipe-separated
\texttt{SELECT} output.  Requirement~\#3 of
\texttt{requirements4.txt} reverses that decision: ``Access the
Postgres database programmatically, not through scripts.''  The
revised design therefore links \texttt{libpq} (Postgres's C
client library, autodetected via \texttt{pg\_config} in the
Makefile) and reaches the database through the standard
\code{PQ*} call surface --- \code{PQconnectdb},
\code{PQprepare}, \code{PQexecPrepared}, \code{PQexecParams}.
This (a)~eliminates the shell quoting and \texttt{popen}
\texttt{SIGPIPE} hazards of the previous design,
(b)~lets duplicate inserts be absorbed one row at a time by an
\texttt{ON~CONFLICT~DO~NOTHING} clause without aborting the
batch (the \texttt{COPY} path could not), and (c)~replaces the
brittle pipe-separated \texttt{SELECT} output with binary-safe
\code{PGresult} field access.  The cost is one new link-time
dependency on \code{libpq}; the SRS allowlist (\req{REQ-D-04})
is updated accordingly.

\subsection{Why per-row \texttt{INSERT \dots\ ON~CONFLICT}, not \texttt{COPY}?}

Requirement~\#4 of \texttt{requirements4.txt} demands that the
program ``check for duplicates before adding information \dots\
and recover appropriately if data already present.''  A bulk
\texttt{COPY \dots\ FROM~STDIN} cannot satisfy this: the first
row that violates the unique constraint aborts the entire
transaction, taking with it every subsequently-streamed row.
Switching to per-row \texttt{INSERT \dots\ ON CONFLICT
(swimmer, event, swim\_time, swim\_date, meet) DO NOTHING}
makes each insert independently idempotent: a duplicate is a
silent no-op, the run exits~0, nothing is written to standard
error, and any genuinely-new rows in the same invocation are
still persisted.  The cost is $N$ round trips instead of one
streamed transaction, but $N$ is at most a few hundred per
invocation and each insert completes in well under a
millisecond against the local container.

\subsection{Why a date-window field on \texttt{Swimmer}?}

\code{ledecky10}, \code{ledecky12}, and \code{ledecky14} all
demand age-bracket filtering that the USA~Swimming JAQL
endpoint does not directly express.  Storing the date window on
the \code{Swimmer} record (rather than as a separate
command-line flag) keeps the per-swimmer policy in one place
and makes new historical comparisons additive: another swimmer
(or another age window for the same swimmer, as the three
Ledecky entries demonstrate) can be added by appending a single
row to \code{SWIMMERS} with no change to \code{main} ---
exactly the path used to satisfy
requirements4.txt~\#1 and \#1a.

\vfill
\begin{center}
  \small\textit{End of document CAST-SDD-001 Rev.\,1.0}
\end{center}

\end{document}
